Article counts per year figure

### 2022-03-10 article-counts-per-year-figure.Rmd
fixed figure

```{r}
dat %>%
  tidyr::pivot_longer(!year) %>%
  ggplot2::ggplot(ggplot2::aes(x = year, y = value, colour = name)) + ggplot2::geom_point()
ggplot2::ggsave("figures/mr-gwas-counts-scatter.png")
```

>>>>

```{r}
dat %>%
  tidyr::pivot_longer(!year) %>%
  dplyr::filter(year != 2022) %>%
  ggplot2::ggplot(ggplot2::aes(x = year, y = value, fill = name)) + 
  ggplot2::geom_bar(stat = "identity", 
                    position=ggplot2::position_dodge()) + 
  ggplot2::scale_fill_manual(labels = c("GWAS", "MR"), values=c('#999999','#E69F00')) + 
  ggplot2::ylab("Annual publication count") + 
  ggplot2::xlab("Year") + 
  ggplot2::guides(fill = ggplot2::guide_legend("Search terms")) +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 270, vjust = 0.5))

ggplot2::ggsave("figures/mr-gwas-counts.png")
```
